---
title: "R Project 1 - Hello R"
author: "Luis Llanas"
date: "9/16/2020"
output: 
  html_document: 
    highlight: tango
    theme: flatly
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1,846 rows in this dataset, with 3 columns. The variables are dataset, x, and y.



### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here, we are calculating the correlation between 'x' and 'y' in this dataset:
 
```{r cor-star}
dino_data %>%
summarize(r = cor(x,y))

```

### Exercise 4

For this exercise, we are plotting the data for the "circle" dataset

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Here, we are going to calculate the correlation between 'x' and 'y' in the circle dataset
```{r}
dino_data %>%
summarize(r = cor(x,y))

```

### Exercise 5

Here, we are plotting all the datasets. 

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

Here, we are going to generate all the summary correlation coefficients
```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)

```

